# Human Activity Recognition data Analysis
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har.

### Load data
```{r}
trainData <- read.csv("pml-training.csv", header=TRUE,na.strings=c("NA","","#DIV/0!"))
testData <- read.csv("pml-testing.csv", header=TRUE, na.strings=c("NA","","#DIV/0!"))
```

### Clear data
We get rid from first seven features cause first we don't need some of them and second: for example num_window answers the question so no application for machine learning. Also many feature are NA in test set? so we find and remove them from both sets

```{r}
all.na <- sapply(testData, function(x) all(is.na(x)))

trainData <- trainData[,which(!all.na)][-c(1:7)]
testData <- testData[,which(!all.na)][-c(1:7)]

trainData$classe <- as.factor(trainData$classe)
```
## Buid model
We create model using caret package, random forest algorithm and ten-fold cross validation. (time consuming process so cache the result). To estimate out-of-sample error we split training set in two parts (70/30).

```{r, cache=TRUE}
set.seed(2334)

library(caret)
inTrain <- createDataPartition(trainData$classe, p=0.70,list=FALSE)
training <- trainData[inTrain,]
testing <- trainData[-inTrain,]

tc <- trainControl(method = "cv", number = 10)

modFit <- train(
  training$classe ~ ., 
  data=training[,-dim(training)[2]], 
  method="rf", 
  trControl = tc,
  prox=TRUE
  )
```

## Make some prediction and estimate out of sample error
```{r}
library(caret)
pred <- predict(modFit,testing[,-dim(testing)[2]])
cm <- confusionMatrix(pred, testing$classe)
ce.out <- 1 - cm$overall["Accuracy"][[1]]
print(cm)
```
### Out-of-sample Error `r ce.out`


